BEX3012 Project Analysis

### 2017-05-05 Internship/EmotionsAnalysis.Rmd
Player subset updates

###
Join emotions for each face
J2: Table of FileNames and associated dominant emotion
```{r combined}
S1 <- select(SBPCL1, FileName = aname , SEmotion = Emotion)
S2 <- select(MEPCL1, FileName, MEmotion = Emotion)
S3 <- select(GEPCL1, FileName, GEmotion = Emotion)
J1 <- full_join(S1, S2, by = "FileName")
J2 <- full_join(J1, S3, by = "FileName")

@@

Player Subsetting
```{r DisplayFaces}

MSimgsG<-GEPCL1 %>% filter(player1=="ARadwanska")
MSimgsG <-MSimgsG %>% filter(detect=="Player")
MSlist <- as.list(MSimgsG$FileName)
length(MSlist)

library(imager)
DisplayFaces <- function(list) {
for (i in 1:length(list)){

@@

>>>>

###
Join emotions for each face
J2: Table of FileNames and associated dominant emotion
```{r combined}
S1 <- select(SBP1, FileName = aname , SEmotion = Emotion)
S2 <- select(MEP1, FileName, MEmotion = Emotion)
S3 <- select(GEP1, FileName, GEmotion = Emotion)
J1 <- full_join(S1, S2, by = "FileName")
J2 <- full_join(J1, S3, by = "FileName")

@@

Player Subsetting
```{r DisplayFaces}
AKimgsG<-GEP %>% filter(player1=="JSousa")
AKimgsG<-AKimgsG %>% filter(detect=="Player")
AKlist <- as.list(AKimgsG$FileName)
length(AKlist)

DisplayFaces(AKlist)

library(imager)
DisplayFaces <- function(list) {
    for (i in 1:15){

@@

``` {r playerSpecificEmotions}
player <- "AMurray"
GEPAM <- GEP %>% filter(playerName == player)
MEPAM <- MEP %>% filter(playerName == player)
SBPAM <- SBP %>% filter(playerName == player)
